### 2022-04-30 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@894682181004ff71027b7be4f20ce0c86e79676e 🚀

The use of the natural variation of \textbf{stable isotopes} (F) as
empirical evidence of the use of trophic resources is based on the study
of isotopic signatures; the isotopic signature of δ15N informs about the
trophic level of the invertebrate and that of δ13C will indicate the
proportion of trophic resources consumed, but the potential trophic
resources need to be chosen previously to the isotopic analysis. (Tiunov
2007; Maraun et al.~2011; Potapov, Tiunov, and Scheu 2019; Potapov et
al.~2019) also, the potential of this tool is such that inferences can
even be made about the metabolic pathways of biomolecules (Pollierer et.
Al. 2019, Pollierer \& Scheu 2021; Chamberlain et. Al. 2006).

>>>>

The use of the natural variation of \textbf{stable isotopes} (F) as
empirical evidence of the use of trophic resources is based on the study
of isotopic signatures; the isotopic signature of \$\delta\$15N informs
about the trophic level of the invertebrate and that of \$\delta\$13C
will indicate the proportion of trophic resources consumed, but the
potential trophic resources need to be chosen previously to the isotopic
analysis. (Tiunov 2007; Maraun et al.~2011; Potapov, Tiunov, and Scheu
2019; Potapov et al.~2019) also, the potential of this tool is such that
inferences can even be made about the metabolic pathways of biomolecules
(Pollierer et. Al. 2019, Pollierer \& Scheu 2021; Chamberlain et. Al.
2006).
